Towards Verifying the Bitcoin-S Library

### 2019-06-20 paper/paper.tex
add references

%\usepackage{courier}
\usepackage{listings}
\usepackage[dvipsnames]{xcolor}
\colorlet{link}{MidnightBlue}
\hypersetup{
  colorlinks   = true,
  linkbordercolor=link,
  pdfborderstyle={/S/U/W .5},% border style will be underline of width 1pt
     linkcolor  = link,
     citecolor  = link,
     urlcolor   = link
}

@@

kai: successor of Leon verifier \cite{DBLP:conf/pldi/VoirolKK15,DBLP:conf/pldi/BlancK15}

>>>>

%\usepackage{courier}
\usepackage{listings, color}
\hypersetup{
  colorlinks   = true,
  linkcolor  = blue,
  citecolor  = blue,
  urlcolor   = blue
}

@@

kai: successor of Leon verifier \cite{DBLP:conf/ecoop/BlancKKS13,DBLP:conf/pldi/VoirolKK15,DBLP:conf/pldi/BlancK15}
